Consistency scores in text data

### 2020-08-05 outputs/documents/paper.Rmd
BERT implementation WIP

OpenAI has made GPT-2 open-sourced through Github with Python and Tensorflow. There is also a package in R that wraps the Python code into a R package, created by @keydanaluraschi2019gpt2. However, the R package only permits exploratory experiments with the pre-trained tasks; fine-tuning for new tasks is not available thorough R. In our project, we aim to use fine-tune GPT-2 to perform a text cleaning task.

@@

Because BERT employs the Transformer architecture with the self-attention mechanism, fine-tuning is also available with one additional output layer and a task-specific input (@devlin2018bert). Google AI researchers have fine-tuned BERT for 11 NLP tasks including question-answering and common-sense inference.

>>>>

OpenAI has made GPT-2 open-sourced through Github with Python and Tensorflow. There is also a package in R that wraps the Python code into a R package, created by @keydanaluraschi2019gpt2. There are three choices of models in terms of parameter sizes — "124M", "355M" and "774M". The R package only permits exploratory experiments with the pre-trained tasks; fine-tuning for new tasks is not available thorough R. To proceed with the implementation of GPT-2 in R, we will fine-tune the model through Python and create a wrapper code for R (**Keli to check if this is possible**).

@@

BERT was pre-trained on BooksCorpus data set with 800 million words and English Wikipedia with 2,500 million words (@devlin2018bert). Because BERT employs the Transformer architecture with the self-attention mechanism, fine-tuning is also available with one additional output layer and a task-specific input (@devlin2018bert). Google AI researchers have fine-tuned BERT for 11 NLP tasks including question-answering and common-sense inference.
